On verifying AhirV2 generated VHDL using software testbenches

### 2018-03-07 Documents/AhirV2/AhirV2.tex
Updated the tutorial etc.

\documentclass[12pt]{article}
\usepackage{epsfig}

@@

The flow of transformations is illustrated in Figure \ref{fig:AhirFlow}.
\begin{figure}
\begin{centering}
\centerline{\psfig{figure=AHIRv2Flow.eps,width=3.0in,height=3.0in}}
\caption{AhirV2 flow}
 \label{fig:AhirFlow}
\end{centering}
\end{figure}

@@

Finally, we take the \vC description and convert it to
VHDL
\begin{verbatim}
vc2vhdl -t add -f add.o.aa.vc | vhdlFormat > system.vhdl
\end{verbatim}
This produces a VHDL implementation of the system with
{\bf add} marked as a top-level module.  The VHDL that
is produced is too voluminous to reproduce here, but
the top-level system entity is
\begin{verbatim}
entity test_system is  -- system
  port (--
    add_a : in  std_logic_vector(31 downto 0);
    add_b : in  std_logic_vector(31 downto 0);
    add_ret_val_x_x : out  std_logic_vector(31 downto 0);
    add_tag_in: in std_logic_vector(0 downto 0);
    add_tag_out: out std_logic_vector(0 downto 0);
    add_start_req : in std_logic;
    add_start_ack : out std_logic;
    add_fin_req   : in std_logic;
    add_fin_ack   : out std_logic;
    clk : in std_logic;
    reset : in std_logic); --
  --
end entity;
\end{verbatim}

@@

One can also map this pipeline to a VHDL system, using the
following flow.  One uses the standard flow that has already
been described:
\begin{verbatim}
clang -std=gnu89 -I../../../iolib/ -emit-llvm -c prog.c
llvm2aa prog.o | vcFormat >  prog.o.aa
Aa2VC -O -I mempool -C prog.o.aa | vcFormat > prog.o.aa.vc
vc2vhdl -C -s ghdl -T foo -T bar -f prog.o.aa.vc\
           | vhdlFormat > system.vhdl
\end{verbatim}
Note that in this case, we use the -T option in vc2vhdl to
specify that foo and bar are free-running top-level modules.
\begin{figure}
\begin{centering}
\centerline{\psfig{figure=FooBarPipeline.eps,width=3.0in,height=3.0in}}
\caption{Hardware implementation of Foo-Bar pipeline}
 \label{fig:FooBarPipeline}
\end{centering}
\end{figure}
The resulting AHIR system in system.vhdl implements the pipeline
(the block diagram of the system is shown in Figure \ref{fig:FooBarPipeline})
with the following interface:
\begin{verbatim}
entity test_system is  -- system 
  port (-- 
    clk : in std_logic;
    reset : in std_logic;
    inpipe_pipe_write_data: in std_logic_vector(31 downto 0);
    inpipe_pipe_write_req : in std_logic_vector(0 downto 0);
    inpipe_pipe_write_ack : out std_logic_vector(0 downto 0);
    outpipe_pipe_read_data: out std_logic_vector(31 downto 0);
    outpipe_pipe_read_req : in std_logic_vector(0 downto 0);
    outpipe_pipe_read_ack : out std_logic_vector(0 downto 0)); -- 
  -- 
end entity;
\end{verbatim}
The system has interfaces corresponding to the pipes inpipe and
outpipe through which data is exchanged.

@@

If you look at the generated top-level VHDL entity, its ports
will be
\begin{verbatim}
entity test_system is  -- system
  port (--
    clk : in std_logic;
    reset : in std_logic;

@@

In this example, we are saying that the shared memory pool
variable is named mempool, and it is an array of 1024 {\bf bytes}.
The generated top-level VHDL entity has the following
ports:
\begin{verbatim}
entity test_system is  -- system
  port (--
    foo_b : in  std_logic_vector(31 downto 0);
    foo_ret_val_x_x : out  std_logic_vector(31 downto 0);
    foo_tag_in: in std_logic_vector(0 downto 0);
    foo_tag_out: out std_logic_vector(0 downto 0);
    foo_start : in std_logic;
    foo_fin   : out std_logic;
    mem_load_x_x_address : in  std_logic_vector(31 downto 0);
    mem_load_x_x_data : out  std_logic_vector(7 downto 0);
    mem_load_x_x_tag_in: in std_logic_vector(0 downto 0);
    mem_load_x_x_tag_out: out std_logic_vector(0 downto 0);
    mem_load_x_x_start_req : in std_logic;
    mem_load_x_x_start_ack : out std_logic;
    mem_load_x_x_fin_req   : in std_logic;
    mem_load_x_x_fin_ack   : out std_logic;
    mem_store_x_x_address : in  std_logic_vector(31 downto 0);
    mem_store_x_x_data : in  std_logic_vector(7 downto 0);
    mem_store_x_x_tag_in: in std_logic_vector(0 downto 0);
    mem_store_x_x_tag_out: out std_logic_vector(0 downto 0);
    mem_store_x_x_start_req : in std_logic;
    mem_store_x_x_start_ack : out std_logic;
    mem_store_x_x_fin_req   : in std_logic;
    mem_store_x_x_fin_ack   : out std_logic;
    clk : in std_logic;
    reset : in std_logic); --
  --
end entity;
\end{verbatim}

@@

If the programs being linked contain memory initialization
routines, the linker generates a global storage initialization
function which is named {\bf global\_storage\_initializer\_}.
This global initializer calls all the memory initializers in
the programs being linked.

@@

The options:
\begin{itemize}
\item {\bf -t} : to specify the modules which are to be 
accessible from the ports of the generated VHDL system.
Such modules have to be top-level (that is, they cannot
be called from within the program).
Multiple top-level modules can be specified in this way.
The control and argument ports for these modules are
visible at the interface of the generated AHIR system.
\item {\bf -T} : to specify top-level modules which are to be 
free-running inside the AHIR system.
Multiple top-level modules can be specified in this way.
Such modules do not have any arguments and do not return
any values.  Their only mechanism of communication with
the world outside the AHIR system is through pipes.
The control ports for these modules are
{\bf not visible} at the interface of the generated AHIR system.
In the AHIR system, these modules are started on reset
and are run forever (restarted after they finish, forever).
\item {\bf -f file-name} : specifies the \vC files to be analyzed. 
Multiple \vC files may be specified.  An object must be
defined before it is used, so the \vC files must be 
specified in the correct order.
\item {\bf -O} : optimize the generated VHDL by compacting
the control-path.  This does not change the resulting
hardware, but makes the generated VHDL file smaller.
\item {\bf -C} : the VHDL code has a system test bench which
interfaces to foreign code using a VHPI/Modelsim-FLI interface.
If this is not specified, the  generated test bench simply
instantiates the system and starts all top-level modules
off (you will need to fill in your own test bench here).
The C testbench is usually easier to write (it probably
already exists in the form of the original program).
\item {\bf -a} : try to minimize the area of the resulting
VHDL by sharing operators to the maximum extent possible
(allowing potential contention for resources).  This will
result in a slower (usually by 2X) system, but will
also reduce the area (usually by 0.5X).  If not specified,
two operations will be mapped to the same
operator  only if it can be proved that they cannot be active simultaneously.
\item {\bf -q } : if specified, do aggressive register insertion
to minimize the clock period.
\item {\bf -S bypass-stride } : by specifying the bypass stride
(an integer $\geq 1$),
the user can trade-off clock cycles versus clock period.  
The lowest clock period will be obtained for -S 1.   
\item {\bf -e top-entity-name} : The generated top-level VHDL entity
corresponding to the AHIR system is named top-entity-name.  The default
is test\_system.
\item {-L function-library} : AhirV2 provides some built in operator
functions which can be called from your code.  These are organized
as function libraries and this option specifies a function library
to look into when generating VHDL.  For example {\em -L fpu} gives
access to the floating point library which provides some useful
built in functions (e.g. fpalu32, fpalu64 etc.).
\item {\bf -w} :  If specified, the VHDL system and test-bench are
generated as separate unformatted VHDL files.  You will need to
format these using the vhdlFormat command.
\item {\bf -s ghdl/modelsim} :  If {\bf ghdl} is specified
with the -s option, then the generated testbench (if -C is specified)
uses the VHPI interface to link with foreign code.  Otherwise,
the generated testbench (if -C is specified) uses the Modelsim FLI
interface to link with foreign code.
\end{itemize}

>>>>

\documentclass[12pt]{article}
\usepackage{epsfig}
\usepackage{graphics}

@@

The flow of transformations is illustrated in Figure \ref{fig:AhirFlow}.
\begin{figure}
\begin{centering}
\centerline{\psfig{figure=AHIRv2Flow.eps,width=3.0in,height=3.0in}}
\caption{AhirV2 flow}
\end{centering}
 \label{fig:AhirFlow}
\end{figure}

@@

Finally, we take the \vC description and convert it to
VHDL
\begin{verbatim}
vc2vhdl -t add -f add.o.aa.vc | vhdlFormat > system.vhdl
\end{verbatim}
This produces a VHDL implementation of the system with
{\bf add} marked as a top-level module.  The VHDL that
is produced is too voluminous to reproduce here, but
the top-level system entity is
\begin{verbatim}
entity ahir_system is  -- system
  port (--
    add_a : in  std_logic_vector(31 downto 0);
    add_b : in  std_logic_vector(31 downto 0);
    add_ret_val_x_x : out  std_logic_vector(31 downto 0);
    add_tag_in: in std_logic_vector(0 downto 0);
    add_tag_out: out std_logic_vector(0 downto 0);
    add_start_req : in std_logic;
    add_start_ack : out std_logic;
    add_fin_req   : in std_logic;
    add_fin_ack   : out std_logic;
    clk : in std_logic;
    reset : in std_logic); --
  --
end entity;
\end{verbatim}

@@

One can also map this pipeline to a VHDL system, using the
following flow.  One uses the standard flow that has already
been described:
\begin{verbatim}
clang -std=gnu89 -I../../../iolib/ -emit-llvm -c prog.c
llvm2aa prog.o | vcFormat >  prog.o.aa
Aa2VC -O -I mempool -C prog.o.aa | vcFormat > prog.o.aa.vc
vc2vhdl -C -s ghdl -T foo -T bar -f prog.o.aa.vc\
           | vhdlFormat > system.vhdl
\end{verbatim}
Note that in this case, we use the -T option in vc2vhdl to
specify that foo and bar are free-running top-level modules.
\begin{figure}
\begin{centering}
\centerline{\psfig{figure=FooBarPipeline.eps,width=3.0in,height=3.0in}}
\caption{Hardware implementation of Foo-Bar pipeline}
 \label{fig:FooBarPipeline}
\end{centering}
\end{figure}
The resulting AHIR system in system.vhdl implements the pipeline
(the block diagram of the system is shown in Figure \ref{fig:FooBarPipeline})
with the following interface:
\begin{verbatim}
entity ahir_system is  -- system 
  port (-- 
    clk : in std_logic;
    reset : in std_logic;
    inpipe_pipe_write_data: in std_logic_vector(31 downto 0);
    inpipe_pipe_write_req : in std_logic_vector(0 downto 0);
    inpipe_pipe_write_ack : out std_logic_vector(0 downto 0);
    outpipe_pipe_read_data: out std_logic_vector(31 downto 0);
    outpipe_pipe_read_req : in std_logic_vector(0 downto 0);
    outpipe_pipe_read_ack : out std_logic_vector(0 downto 0)); -- 
  -- 
end entity;
\end{verbatim}
The system has interfaces corresponding to the pipes inpipe and
outpipe through which data is exchanged.

@@

If you look at the generated top-level VHDL entity, its ports
will be
\begin{verbatim}
entity ahir_system is  -- system
  port (--
    clk : in std_logic;
    reset : in std_logic;

@@

In this example, we are saying that the shared memory pool
variable is named mempool, and it is an array of 1024 {\bf bytes}.
The generated top-level VHDL entity has the following
ports:
\begin{verbatim}
entity ahir_system is  -- system
  port (--
    foo_b : in  std_logic_vector(31 downto 0);
    foo_ret_val_x_x : out  std_logic_vector(31 downto 0);
    foo_tag_in: in std_logic_vector(0 downto 0);
    foo_tag_out: out std_logic_vector(0 downto 0);
    foo_start : in std_logic;
    foo_fin   : out std_logic;
    mem_load_x_x_address : in  std_logic_vector(31 downto 0);
    mem_load_x_x_data : out  std_logic_vector(7 downto 0);
    mem_load_x_x_tag_in: in std_logic_vector(0 downto 0);
    mem_load_x_x_tag_out: out std_logic_vector(0 downto 0);
    mem_load_x_x_start_req : in std_logic;
    mem_load_x_x_start_ack : out std_logic;
    mem_load_x_x_fin_req   : in std_logic;
    mem_load_x_x_fin_ack   : out std_logic;
    mem_store_x_x_address : in  std_logic_vector(31 downto 0);
    mem_store_x_x_data : in  std_logic_vector(7 downto 0);
    mem_store_x_x_tag_in: in std_logic_vector(0 downto 0);
    mem_store_x_x_tag_out: out std_logic_vector(0 downto 0);
    mem_store_x_x_start_req : in std_logic;
    mem_store_x_x_start_ack : out std_logic;
    mem_store_x_x_fin_req   : in std_logic;
    mem_store_x_x_fin_ack   : out std_logic;
    clk : in std_logic;
    reset : in std_logic); --
  --
end entity;
\end{verbatim}

@@

If the programs being linked contain memory initialization
routines, the linker generates a global storage initialization
function which is named 
\begin{verbatim}
global_storage_initializer
\end{verbatim}
This global initializer calls all the memory initializers in
the programs being linked.

@@

The options:
\begin{itemize}
\item {\bf -t} : to specify the modules which are to be 
accessible from the ports of the generated VHDL system.
Such modules have to be top-level (that is, they cannot
be called from within the program).
Multiple top-level modules can be specified in this way.
The control and argument ports for these modules are
visible at the interface of the generated AHIR system.
\item {\bf -T} : to specify top-level modules which are to be 
free-running inside the AHIR system.
Multiple top-level modules can be specified in this way.
Such modules do not have any arguments and do not return
any values.  Their only mechanism of communication with
the world outside the AHIR system is through pipes.
The control ports for these modules are
{\bf not visible} at the interface of the generated AHIR system.
In the AHIR system, these modules are started on reset
and are run forever (restarted after they finish, forever).
\item {\bf -f file-name} : specifies the \vC files to be analyzed. 
Multiple \vC files may be specified.  An object must be
defined before it is used, so the \vC files must be 
specified in the correct order.
\item {\bf -O} : optimize the generated VHDL by compacting
the control-path.  This does not change the resulting
hardware, but makes the generated VHDL file smaller.
\item {\bf -C} : the VHDL code has a system test bench which
interfaces to foreign code using a VHPI/Modelsim-FLI interface.
If this is not specified, the  generated test bench simply
instantiates the system and starts all top-level modules
off (you will need to fill in your own test bench here).
The C testbench is usually easier to write (it probably
already exists in the form of the original program).
\item {\bf -a} : try to minimize the area of the resulting
VHDL by sharing operators to the maximum extent possible
(allowing potential contention for resources).  This will
result in a slower (usually by 2X) system, but will
also reduce the area (usually by 0.5X).  If not specified,
two operations will be mapped to the same
operator  only if it can be proved that they cannot be active simultaneously.
\item {\bf -q } : if specified, do aggressive register insertion
to minimize the clock period.
\item {\bf -S bypass-stride } : by specifying the bypass stride
(an integer $\geq 1$),
the user can trade-off clock cycles versus clock period.  
The lowest clock period will be obtained for -S 1.   
\item {\bf -e top-entity-name} : The generated top-level VHDL entity
corresponding to the AHIR system is named top-entity-name.  The default
is ahir\_system.
\item {-L function-library} : AhirV2 provides some built in operator
functions which can be called from your code.  These are organized
as function libraries and this option specifies a function library
to look into when generating VHDL.  For example {\em -L fpu} gives
access to the floating point library which provides some useful
built in functions (e.g. fpalu32, fpalu64 etc.).
\item {\bf -w} :  If specified, the VHDL system and test-bench are
generated as separate unformatted VHDL files.  You will need to
format these using the vhdlFormat command.
\item {\bf -s ghdl/modelsim} :  If {\bf ghdl} is specified
with the -s option, then the generated testbench (if -C is specified)
uses the VHPI interface to link with foreign code.  Otherwise,
the generated testbench (if -C is specified) uses the Modelsim FLI
interface to link with foreign code.
\end{itemize}

### 2018-03-07 Documents/Tutorials/Intro/Intro.tex
Updated.
Updated the tutorial etc.

Go to ex1/ and check it out.

@@

\frame[containsverbatim]{\frametitle{VHDL Structure}
\begin{figure}
  \centering
  \includegraphics[width=10cm]{ex1/figs/VhdlStructure.eps}
  \caption{VHDL structure of generated example}
\end{figure}
}

@@

\frame[containsverbatim]{\frametitle{Download and Install}
\begin{itemize}
\item Clone git repository
\begin{verbatim}
git clone https://github.com/madhavPdesai/ahir.git .
\end{verbatim}
\item Install llvm-2.8, clang-2.8 from www.llvm.org (from source, builds on ubuntu 12, centos 6.5, may need  to do minor edits in includes in ubuntu 14).
\item Install boost development packages.
\item Install antlr-2.7.7 (from source, builds on ubuntu 12, centos 6.5, some includes need to be added in ubuntu 14).
\item Install java run-time (openjdk).
\item Install ghdl (or modelsim).
\item Go to release directory. 
\begin{verbatim}
source ahir_bashrc
mkdir bin
./build.sh
\end{verbatim}
\item Should work..
\end{itemize}
}

>>>>

Go to ex1/ and check it out.
\begin{itemize}
\item In the Makefile, we define rules to produce a ``software'' executable (testbench\_sw)
and two ``hardware'' executables, testbench\_hw  and ahir\_system\_test\_bench.
\item You can execute testbench\_sw to verify that your C code is OK.
\item You can concurrently execute testbench\_hw and ahir\_system\_test\_bench to
verify that the the VHDL is OK.
\item Note: the same testbench.c file is used to verify both the software and hardware.
\end{itemize}

@@

\frame[containsverbatim]{\frametitle{VHDL Structure}
\begin{figure}
  \centering
  \includegraphics[width=10cm]{ex1/figs/VhdlStructure.pdf}
  \caption{VHDL structure of generated example}
\end{figure}
}

@@

\frame[containsverbatim]{\frametitle{Download and Install}
\begin{itemize}
\item Clone git repository
\begin{verbatim}
git clone https://github.com/madhavPdesai/ahir.git .
\end{verbatim}
\item Install llvm-2.8, clang-2.8 from www.llvm.org (from source, builds on ubuntu 12, centos 6.5, may need  to do minor edits in includes in ubuntu 14).
\item Install boost development packages, GNU pth, pdflatex (packages exist for ubuntu/centos).
\item Install antlr-2.7.7 (from source, builds on ubuntu 12, centos 6.5, some includes need to be added in ubuntu 14).
\item Install java run-time (openjdk).
\item Install ghdl (or modelsim).
\item Go to release directory. 
\begin{verbatim}
source ahir_bashrc
mkdir bin
./build.sh
\end{verbatim}
\item Should work..
\end{itemize}
}

### 2018-03-07 v2/CtestBench/docs/CtestBench.tex
Updated the tutorial etc.

Obviously, we would prefer to use the same test-bench
to verify that the VHDL system generated from ``prog.c'' 
functions correctly.  
The difference is that instead of using the pipeHandler,
the test-bench now uses methods in SocketLib.  Further, the
VHDL is executed in a VHDL simulator; the simulator communicates
with the testbench using sockets.
The {\em ifdef's} in the test-bench and the system program
indicate the difference between the pure software version
of the system-test-bench combination and the hardware-software
version.

The following Makefile builds a software-only testbench
executable, and also converts the system described in prog.c
to VHDL.  The same testbench can be used to test the VHDL
also.
\begin{verbatim}
# build software version of testbench (to check the "desired behaviour")
SOCKETLIB_INCLUDE=$(AHIR_RELEASE)/CtestBench/include
SOCKETLIB_LIB=$(AHIR_RELEASE)/CtestBench/lib
PIPEHANDLER_INCLUDE=$(AHIR_RELEASE)/pipeHandler/include
PIPEHANDLER_LIB=$(AHIR_RELEASE)/pipeHandler/lib
PTHREADUTILS_INCLUDE=$(AHIR_RELEASE)/pthreadUtils/include
VHDL_LIB=$(AHIR_RELEASE)/vhdl
VHDL_VHPI_LIB=$(AHIR_RELEASE)/CtestBench/vhdl
FUNCTIONLIB=$(AHIR_RELEASE)/functionLibrary/
SRC=./src
all: SW HW 
TOAA:c2llvmbc llvmbc2aa  aalink
TOVC:c2llvmbc llvmbc2aa  aalink aa2vc 
VC2VHDL: vc2vhdl  vhdlsim
AA2VHDLSIM: aa2vc  vc2vhdl  vhdlsim
TOVHDL:TOVC vc2vhdl

@@

# compile with SW defined.
# note the use of IOLIB in building the testbench.
SW: $(SRC)/prog.c $(SRC)/prog.h $(SRC)/testbench.c 
	gcc -g -c -DSW $(PROGDEFS) -I$(PIPEHANDLER_INCLUDE)\
              -I$(FUNCTIONLIB)/include -I$(SRC) $(SRC)/prog.c
	gcc -g -c -DSW $(PROGDEFS) -I$(PIPEHANDLER_INCLUDE)\
              -I$(PTHREADUTILS_INCLUDE) -I$(SRC) $(SRC)/testbench.c
	gcc -g -o testbench_sw prog.o testbench.o\
              -L$(PIPEHANDLER_LIB) -lPipeHandler -lpthread

@@

# C to llvm byte-code.. use clang.
c2llvmbc: $(SRC)/prog.c $(SRC)/prog.h
	clang -O3 -std=gnu89 $(PROGDEFS)  -I$(SOCKETLIB_INCLUDE)\
              -I$(FUNCTIONLIB)/include -emit-llvm -c $(SRC)/prog.c
	opt --indvars --loopsimplify prog.o -o prog.opt.o
	llvm-dis prog.opt.o

@@

vhdlTb: $(SRC)/testbench.c vhdlCStubs.h vhdlCStubs.c
	gcc -c vhdlCStubs.c  -I$(SRC)\
                -I./ -I$(SOCKETLIB_INCLUDE)
	gcc -c $(SRC)/testbench.c\
                -I$(PTHREADUTILS_INCLUDE) -I$(SRC)\
                -I./ -I$(SOCKETLIB_INCLUDE)
	gcc -o testbench_hw testbench.o vhdlCStubs.o\
                -L$(SOCKETLIB_LIB) -lSocketLib -lpthread

ghdlModel: ahir_system.vhdl ahir_system_test_bench.vhdl ahir_system_global_package.vhdl
	ghdl --clean
	ghdl --remove
	ghdl -i --work=GhdlLink  $(VHDL_LIB)/GhdlLink.vhdl
	ghdl -i --work=ahir  $(VHDL_LIB)/ahir.vhdl
	ghdl -i --work=aHiR_ieee_proposed\
                $(VHDL_LIB)/aHiR_ieee_proposed.vhdl
	ghdl -i --work=work ahir_system_global_package.vhdl
	ghdl -i --work=work ahir_system.vhdl
	ghdl -i --work=work ahir_system_test_bench.vhdl
	ghdl -m --work=work -Wl,-L$(SOCKETLIB_LIB) -Wl,-lVhpi ahir_system_test_bench

>>>>

Obviously, we would prefer to use the same test-bench
to verify that the VHDL system generated from ``prog.c'' 
functions correctly.  
The difference is that instead of using the pipeHandler,
the test-bench now uses methods in SocketLibPipeHandler.  Further, the
VHDL is executed in a VHDL simulator; the simulator communicates
with the testbench using sockets.
The {\em ifdef's} in the test-bench and the system program
indicate the difference between the pure software version
of the system-test-bench combination and the hardware-software
version.

The following Makefile builds a software-only testbench
executable, and also converts the system described in prog.c
to VHDL.  The same testbench can be used to test the VHDL
also.
\begin{verbatim}
# build software version of testbench (to check the "desired behaviour")
AHIR_INCLUDE=$(AHIR_RELEASE)/include
AHIR_LIB=$(AHIR_RELEASE)/lib
VHDL_LIB=$(AHIR_RELEASE)/vhdl
VHDL_VHPI_LIB=$(AHIR_RELEASE)/vhdl
FUNCTIONLIB=$(AHIR_RELEASE)/functionLibrary/
SRC=./src
all: SW HW 
TOAA:c2llvmbc llvmbc2aa  aalink
TOVC:c2llvmbc llvmbc2aa  aalink aa2vc 
VC2VHDL: vc2vhdl  vhdlsim
AA2VHDLSIM: aa2vc  vc2vhdl  vhdlsim
TOVHDL:TOVC vc2vhdl

@@

# compile with SW defined.
# note the use of IOLIB in building the testbench.
SW: $(SRC)/prog.c $(SRC)/prog.h $(SRC)/testbench.c 
	gcc -g -c -DSW $(PROGDEFS) -I$(AHIR_INCLUDE)\
              -I$(FUNCTIONLIB)/include -I$(SRC) $(SRC)/prog.c
	gcc -g -c -DSW $(PROGDEFS) -I$(AHIR_INCLUDE)\
               -I$(SRC) $(SRC)/testbench.c
	gcc -g -o testbench_sw prog.o testbench.o\
              -L$(AHIR_LIB) -lPipeHandler -lpthread

@@

# C to llvm byte-code.. use clang.
c2llvmbc: $(SRC)/prog.c $(SRC)/prog.h
	clang -O3 -std=gnu89 $(PROGDEFS)  -I$(AHIR_INCLUDE)\
              -I$(FUNCTIONLIB)/include -emit-llvm -c $(SRC)/prog.c
	opt --indvars --loopsimplify prog.o -o prog.opt.o
	llvm-dis prog.opt.o

@@

vhdlTb: $(SRC)/testbench.c vhdlCStubs.h vhdlCStubs.c
	gcc -c vhdlCStubs.c  -I$(SRC)\
                -I./ -I$(AHIR_INCLUDE)
	gcc -c $(SRC)/testbench.c\
                -I$(AHIR_INCLUDE) -I$(SRC)\
                -I./ 
	gcc -o testbench_hw testbench.o vhdlCStubs.o\
                -L$(AHIR_LIB) -lSocketLibPipeHandler -lpthread

ghdlModel: ahir_system.vhdl ahir_system_test_bench.vhdl ahir_system_global_package.vhdl
	ghdl --clean
	ghdl --remove
	ghdl -i --work=GhdlLink  $(VHDL_LIB)/GhdlLink.vhdl
	ghdl -i --work=ahir  $(VHDL_LIB)/ahir.vhdl
	ghdl -i --work=aHiR_ieee_proposed\
                $(VHDL_LIB)/aHiR_ieee_proposed.vhdl
	ghdl -i --work=work ahir_system_global_package.vhdl
	ghdl -i --work=work ahir_system.vhdl
	ghdl -i --work=work ahir_system_test_bench.vhdl
	ghdl -m --work=work -Wl,-L$(AHIR_LIB) -Wl,-lVhpi ahir_system_test_bench
